Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-03-04 ForegroundSimulations/ms.tex
Update Introduction, add citations to bibliography
From d6a3635 (fgsim):
====================

In eor.bib,

(*) Add two references - Pober et al.(2015, 2016)

In ms.tex,

(*) Update Introduction section

The extreme dynamic range required to subtract foregrounds precisely demands high precision modeling of foregrounds as observed by modern wide-field instruments \citep{thy15a,thy15b}. Their studies of effects of wide-field measurements of EoR power spectra have demonstrated the {\it pitchfork} effect wherein foreshortening of baselines causes a prominent enhancement of foreground power near the horizon limits of the {\it foreground wedge} as well in the contamination beyond. In this paper, we explore yet another phenomenon that inherently extends foreground power beyond the {\it wedge}, namely, that arising from the chromaticity of the antenna power pattern. % We specifically use the current design of 14~m dish of HERA as an example in our study.

This paper is organized as follows. \S\ref{sec:HERA} introduces the HERA instrument. A brief summary of the delay spectrum technique used extensively in this analysis and the recently confirmed {\it pitchfork} effect are presented in \S\ref{sec:delay-spectrum}. \S\ref{sec:sim} describes foreground simulations including antenna beam pattern and all-sky foreground models. \S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on dish reflectometry. Our findings are summarized in \S\ref{sec:summary}.

@@

We reiterate that these estimates are obtained from a conservative scenario wherein only simple spectral weighting technique in the {\it foreground avoidance} limit is used, without any foreground removal or sophisticated weighting strategies using inverse-covariance. Further, these estimates represent worst-case lower limits demonstrating that HERA-19 and its successors will be extremely sensitive for EoR experiments and will benefit even further with more optimal foreground suppression strategies.

>>>>

However, despite attempts to exploit this knowledge about differences in spectral and spatial symmetry in lengthy observations, analysis from the first-generation experiments has at best only led to weak constraints on reionization models \citep{ali15,dil15,pob15}. This is because their sensitivity is primarily limited by instrumental and foreground systematics. The extreme dynamic range required to suppress foreground and instrument systematics demands high precision modeling of foregrounds as observed by modern wide-field instruments. One such study was undertaken by \citet{thy15a,thy15b}. Their studies of effects of wide-field measurements of EoR power spectra have demonstrated the {\it pitchfork} effect wherein foreshortening of baselines causes a prominent enhancement of foreground power near the horizon limits of the {\it foreground wedge} as well as in the contamination beyond. It highlighted the importance of controlling the response of wide-field instruments near the horizon. The need of precise subtraction of foregrounds in wide-field measurements was also highlighted in \citet{pob16}.

In this paper, we explore yet another phenomenon that inherently extends foreground power beyond the {\it wedge}, namely, that arising from the chromaticity of the antenna power pattern. While highlighting the significance of such instrumental systematics on future EoR experiments, we demonstrate that the current HERA instrument design will exceed these specifications to detect the EoR signal with high significance, when data is limited by foregrounds and systematics, even in the most conservative scenario which involves neither foreground subtraction nor optimal analysis techniques but only relies on a simple spectral weighting scheme.

This paper is organized as follows. \S\ref{sec:HERA} introduces the HERA instrument. A brief summary of the delay spectrum technique used extensively in this analysis and the recently confirmed {\it pitchfork} effect are presented in \S\ref{sec:delay-spectrum}. \S\ref{sec:sim} describes foreground simulations including antenna beam pattern and all-sky foreground models. \S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on reflections in the instrument. Lower limits on sensitivity of HERA under conservative conditions are demonstrated in \S\ref{sec:eor-sensitivity}. Our findings are summarized in \S\ref{sec:summary}.

@@

We reiterate that these estimates are obtained in a conservative scenario wherein only simple spectral weighting technique in the {\it foreground avoidance} limit is used, without any foreground removal or sophisticated weighting strategies using inverse-covariance. Further, these estimates represent worst-case lower limits demonstrating that HERA-19 and its successors will be extremely sensitive for EoR experiments and will benefit even further with more optimal foreground suppression strategies.
